---
title: "St. Louis Metro Area Population - 2020 Census"
author: "Jerry Lakin"
date: "8/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading 2020 Census Data

We first load the census data from our .csv file. This file contains county-level
data including 2010 population, 2020 population and the latitude and longitude
of each county. R interprets the population numbers as strings. We convert them 
to numeric format in a new column, taking care to remove comma separators. 

```{r load}
df <- read.csv('stl_metro_2020_population.csv')

df$pop2020 <- as.numeric(gsub(",", "", df$X2020))
df <- subset(df, select = c(County, pop2020, Lat, Lng))

```

## Plotting the Population Density with Leaflet

Next we will use the leaflet package to plot 2020 population data on a map of
the St. Louis metropolitan area.

```{r map, message = FALSE, warning = FALSE}
library(leaflet)
df %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(df$pop2020)*20, popup = df$County)
```